\hyphenation{count-Free-Clusters File-System}

To get the free space left on EFSL 0.2 is a bit tricky. This
feature was implemented after it had gone into stable, so it
couln't interfere with other library functions.

If the filesystem type is FAT12 of FAT16, you must call\\
\code{euint32 fat\_countFreeClusters (FileSystem *fs)} to know
the amount of free clusters. Please note that this is an expensive
function call in terms of speed. It will also work on FAT32 volumes,
but there is a better alternative for that.

Usually FAT32 volumes are substantially larger than FAT12 of FAT16 volumes.
Microsoft, in it's infinite wisdom, decided to use the second sector of
the partition to dump various statistics about the filesystem. Problem
is they are inaccurate, so if you want to be really sure, always use the
beforementioned countFreeClusters function.

To save time, you can also use \code{esint8 fs\_getFsInfo(FileSystem *fs,euint8 force\_update)}.
If force\_update is set to 0, this function will simply gather the data
that is stored on the disc regarding free space. If you call it with
force\_update set to 1, it will gather this data, but correct the result
with a call to countFreeClusters.
After that you will find the result in fs->FreeClusterCount.

To save time, call getFsInfo after you mounted the filesystem,
and just before you umount the filesystem give a call to setFsInfo.
This will make the updated clustercount get written to disc, so you
don't have to go through the lenghty verification everytime.
The functions that have the largest impact on free space (allocClusterChain
and unlinkClusterChain) keep track of the changes they make and they update
the fs->FreeClusterCount field accordingly.

This is an ugly ``add-on'', and will be replaced by a decent implementation
in the 0.3/0.4 series.
